Study of Intra- and Inter-Job Interference with Different Job allocations

### 2015-10-15 submission.tex
minor chage to some citations

The scale of supercomputers keeps growing to accommodate the the demand for computing power required by scientific research areas. Supercomputers have hundreds of thousands of nodes, and serve as irreplaceable research vehicle for scientific problems with increasing size and complexity. Supercomputers are usually employed as a shared resource to accommodate many parallel applications (also known as jobs) running concurrently \cite{zhou-ipdps} and maintain high system utilization. These communication and I/O intensive jobs share the system infrastructure such as network and I/O bandwidth, and inevitably there is contention over these shared resources. As supercomputers continue to evolve, these shared resources are increasingly the bottleneck for performance.

@@

We selected three signature applications from DOE Design Forward Project\cite{designforwardwebpage} as examples to conduct detailed study about their communication patterns. We use a sophisticated simulation toolkit named CODES, Co-Design of Multi-layer Exascale Storage Architecture\cite{Jason-2011}, from Argonne National Laboratory as a research vehicle to evaluate the performance of these applications with various allocations. We analyze the intra- and inter-job interference by simulating these applications running exclusively and concurrently with different allocations. The major finds and insights of this work are the following:

@@

AMG represents a group of applications whose dominant communication pattern is Nearest Neighbor. Applications with such similar dominant communication pattern are like PARTISN, SNAP \cite{designforwardwebpage}.

>>>>

The scale of supercomputers keeps growing to accommodate the the demand for computing power required by scientific research areas. Supercomputers have hundreds of thousands of nodes, and serve as irreplaceable research vehicle for scientific problems with increasing size and complexity. Supercomputers are usually employed as a shared resource to accommodate many parallel applications (also known as jobs) running concurrently \cite{zhou-ipdps}. To be effective, they must maintain high system utilization. These communication and I/O intensive jobs share the system infrastructure such as network and I/O bandwidth, and inevitably there is contention over these shared resources. As supercomputers continue to evolve, these shared resources are increasingly the bottleneck for performance.

@@

We selected three signature applications from DOE Design Forward Project\cite{designforwardwebpage} as examples to conduct detailed study about their communication patterns. We use a sophisticated simulation toolkit named CODES, Co-Design of Multi-layer Exascale Storage Architecture\cite{Jason-2011} from Argonne National Laboratory, as a research vehicle to evaluate the performance of these applications with various allocations. We analyze the intra- and inter-job interference by simulating these applications running exclusively and concurrently with different allocations. The major finds and insights of this work are the following:

@@

AMG represents a group of applications whose dominant communication pattern is Nearest Neighbor. Applications with such similar dominant communication pattern are like PARTISN\cite{designforwardwebpage} and SNAP \cite{designforwardwebpage}.
